---
title: "Problem set 1"
author: "HaEun Choi"
date: 2020-09-25T21:13:14-05:00
bibliography: "references.bib"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

#Abstract
My abstract

# Introduction

We use @citetidyverse.

Three paragraph statement.

First paragraph: General. Motivational. Majors specific finding. 

Second paragraph: More about what you did and found.

Third paragraph: Outline of the paper. Future work. Weaknesses.



```{r download, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
#install.packages("devtools")
library(devtools)
#devtools::install_github("hodgettsp/cesR")
#library(tidyverse)
library(cesR)
get_ces("ces2019_web")
#install.packages("Rcpp")
library("Rcpp")

```


#Data
The CES dataset is

```{r}
get_decon()
mydata=data.frame(decon$province_territory,ces2019_web$cps19_v_likely)
#unique(mydata$ces2019_web.cps19_v_likely)
mydata$vote=ifelse(mydata$ces2019_web.cps19_v_likely==5 | mydata$ces2019_web.cps19_v_likely==6 | is.na(mydata$ces2019_web.cps19_v_likely), NA, ifelse(mydata$ces2019_web.cps19_v_likely==3 | mydata$ces2019_web.cps19_v_likely==4, 0, 1))

```



#Data Discussion
The variables we focus on are....

Summary statistics for these variables...

You must include graphs.




# Graph 

```{r}
#install.packages("ggplot2")
library(ggplot2)
ggplot(mydata, aes(x=decon.province_territory, y=vote)) + stat_summary(fun.y="mean", geom="bar") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_flip()
```



#Weaknesses 



#Nexsteps




# References

- Stephenson, Laura B; Harell, Allison; Rubenson, Daniel; Loewen, Peter John, 2020, '2019 Canadian Election Study - Online Survey', https://doi.org/10.7910/DVN/DUS88V, Harvard Dataverse, V1

- Stephenson, Laura, Allison Harrel, Daniel Rubenson and Peter Loewen. Forthcoming. 'Measuring Preferences and Behaviour in the 2019 Canadian Election Study,' Canadian Journal of Political Science.

-ggplot2: Elegant Graphics for Data Analysis
Wickham, H., 2016. Springer-Verlag New York.

